Inverted Index

### 2023-10-09 latex/paper.tex

The second implementation of the indexer uses the NLTK library.
This python script creates an inverted word index
from a collection of documents in JSON format.
The indexer function is defined to create the inverted word index.
It takes a generator of documents as input. For each document,
it tokenizes the text into words using NLTK and builds the inverted index,
associating words with sets of document identifiers in which those words appear.
With the NLTK library we did not encounter a problem of one million characters limit.
The document\_generator function generates documents from a specified
directory (datalake) containing JSON files.
For each JSON file in the directory, it creates a document identifier
based on the file name and reads the JSON content,
returning it as a tuple of the document identifier and document dictionary.
The script checks the number of command-line arguments.
% fix
It expects exactly one argument, which should be the path to the datalake directory containing JSON documents.
Creating the Inverted Index:
The main part of the code creates the inverted index by
calling the indexer function with documents generated by
the document\_generator function, based on the specified datalake directory.
Saving the Index to "index.txt":
The code creates a text file named "index.txt" and writes the inverted
index data into it. Each line of the file contains a word
followed by a list of document identifiers where that word is found.
Displaying Results in the Terminal:
The script displays the inverted index in the terminal
showing each word along with the document identifiers where it appears.
In summary, this script processes JSON documents from a directory, tokenizes the text into words, and constructs an inverted index. This version of indexer can be used to efficiently search for and index words within the text data in our search engine project.

>>>>

The second implementation of the indexer uses the NLTK library.
This python script creates an inverted word index
from a collection of documents in JSON format.
The indexer function is defined to create the inverted word index.
It takes a generator of documents as input. For each document,
it tokenizes the text into words using NLTK and builds the inverted index,
associating words with sets of document identifiers in which those words appear.
With the NLTK library we did not encounter a problem of one million characters limit.
The document\_generator function generates documents from a specified
directory (datalake) containing JSON files.
For each JSON file in the directory, it creates a document identifier
based on the file name and reads the JSON content,
returning it as a tuple of the document identifier and document dictionary.
The script checks the number of command-line arguments.
% fix
It expects exactly one argument, which should be the path to the datalake directory containing JSON documents.
Creating the Inverted Index:
The main part of the code creates the inverted index by
calling the indexer function with documents generated by
the document\_generator function, based on the specified datalake directory.
Saving the Index to SQLite database:
Create datamart function creates two tables in an SQLite database: "inv index" and "documents". 
The first table stores an inverted index mapping words to document IDs, while the second table stores information about documents, such as their titles, dates, and content. The code writes the inverted index data into it.
In summary, this script processes JSON documents from a directory, tokenizes the text into words, and constructs an inverted index. This version of indexer can be used to efficiently search for and index words within the text data in our search engine project.
